Optimizing Deep Learning Workloads on ARM GPU with TVM

### 2018-06-11 dissemination.publication/8b220a7f172a47d4/paper.tex
improved meta for ACM DL proceedings
final meta updates
added instructions how to use CK snapshot from ACM DL

{\small
\begin{itemize}
  \item {\bf Algorithm:} image classification
  \item {\bf Program:} TVM/NNVM, ARM Compute Library, MXNet, OpenBLAS
  \item {\bf Compilation:} g++
  \item {\bf Binary:} will be compiled on a target platform
  \item {\bf Data set:} ImageNet 2012 validation (50,000 images)
  \item {\bf Run-time environment:} Linux with OpenCL
  \item {\bf Hardware:} Firefly-RK3399 with ARM Mali-T860MP4 or other boards with ARM Mali GPUs
  \item {\bf Run-time state:} set by our scripts
  \item {\bf Metrics:} inference speed; accuracy
  \item {\bf Output:} classification result; execution time; accuracy
  \item {\bf Experiments:} benchmarking the inference speed of different backends on ImageNet (automated via CK command line)
  \item {\bf How much disk space required (approximately)?:} ~4GB
  \item {\bf How much time is needed to prepare workflow (approximately)?:} several hours (mainly native compilation of packages)
  \item {\bf How much time is needed to complete experiments (approximately)?:} hours for full ImageNet accuracy validation (50000 images)
  \item {\bf Publicly available?:} Yes
  \item {\bf Code license?:} 
  \item {\bf Collective Knowledge workflow framework used?:} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm }
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}
  \item {\bf Original artifact URL:} \url{https://github.com/merrymercy/tvm-mali}
\end{itemize}

@@

>>>>

{\small
\begin{itemize}
  \item {\bf Algorithm:} image classification
  \item {\bf Program:} TVM/NNVM, ARM Compute Library, MXNet, OpenBLAS
  \item {\bf Compilation:} g++
  \item {\bf Binary:} will be compiled on a target platform
  \item {\bf Data set:} ImageNet 2012 validation (50,000 images)
  \item {\bf Run-time environment:} Linux with OpenCL
  \item {\bf Hardware:} Firefly-RK3399 with ARM Mali-T860MP4 or other boards with ARM Mali GPUs
  \item {\bf Run-time state:} set by our scripts
  \item {\bf Metrics:} inference speed; accuracy
  \item {\bf Output:} classification result; execution time; accuracy
  \item {\bf Experiments:} benchmarking the inference speed of different backends on ImageNet (automated via CK command line)
  \item {\bf How much disk space required (approximately)?:} ~4GB
  \item {\bf How much time is needed to prepare workflow (approximately)?:} several hours (mainly native compilation of packages)
  \item {\bf How much time is needed to complete experiments (approximately)?:} hours for full ImageNet accuracy validation (50000 images)
  \item {\bf Publicly available?:} Yes
  \item {\bf Code license?:} MIT license
  \item {\bf Collective Knowledge workflow framework used?:} Yes
  \item {\bf CK workflow URL:} \url{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm }
  \item {\bf CK results URL:} \url{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}
  \item {\bf Original artifact URL:} \url{https://github.com/merrymercy/tvm-mali}
\end{itemize}

@@

\subsubsection{Install this CK workflow from the ACM Digital Library snapshot}

It is possible to install and test the snapshot of this workflow 
from the ACM Digital Library without interfering with your current CK installation.
Download related file "request-asplos18-artifact-?-ck-workflow.zip"
to a temporary directory, unzip it and then execute the following commands:

\begin{verbatim}
$ . ./prepare_virtual_ck.sh
$ . ./start_virtual_ck.sh
\end{verbatim}

All CK repositories will be installed in your current directory.
You can now proceed with further evaluation as described below.
